---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# compak: Conway-Maxwell-Poisson Associated Kernal

# compak <img src='man/figures/logo.svg' align="right" height="139" />

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Codecov test coverage](https://codecov.io/gh/thomas-fung/compak/branch/main/graph/badge.svg)](https://codecov.io/gh/thomas-fung/compak?branch=main)
[![R-CMD-check](https://github.com/thomas-fung/compak/workflows/R-CMD-check/badge.svg)](https://github.com/thomas-fung/compak/actions)
<!-- badges: end -->

The `compak` package provided a discrete associated kernel smoother for estimating probability mass functions using the mean-parametrised Conway-Maxwell-Poisson (COMP) distribution of [Huang (2017)](https://doi.org/10.1177%2F1471082X17697749). Two automated bandwidth selection approaches, one based on minimizing Kullback-Leidler divergence and another based on cross-validation, are also implemented. 

## Installation

### Stable release on CRAN

`compak` is not available on [CRAN](https://CRAN.R-project.org) yet.

### Development version on Github

You can use the **devtools** package to install the development version of **compak** from [GitHub](https://github.com/thomas-fung/compak):

```{r, eval= FALSE}
# install.packages("devtools")
devtools::install_github("thomas-fung/compak")
library(compak)
```

## Usage

A reference manual and some examples are available at [thomas-fung.github.io/compak](https://thomas-fung.github.io/compak/).


## Citation

If you use this package to analyse your data, please use the following citation:

- Sippel, L., Fung, T. and Huang, A. (2020). compak: Conway-Maxwell-Poisson associated kernel. R package version 0.0.0.9000.

From R you can use:

```{r, eval=FALSE}
citation("compak")
toBibtex(citation("compak"))
```


